Demonstrating the Reliability of Randomized Measurement and Verification for Switchable Control Retrofits Using a Large Open-Source Dataset

### 2025-04-24 code/manuscript.Rmd
Modified blocking period for new starting time

|                 | Reference study results [@granderson_accuracy_2016] | Our study results      |
|-------------------|-----------------------------------|-------------------|
| 25th percentile | -5.85                                               | `r percentiles$Q1`     |
| 50th percentile | -1.25                                               | `r percentiles$Median` |
| 75th percentile | 3.86                                                | `r percentiles$Q3`     |

@@

>>>>

|                 | Reference study results [@granderson_accuracy_2016] | Our study results      |
|-------------------|----------------------------------|-------------------|
| 25th percentile | -5.85                                               | `r percentiles$Q1`     |
| 50th percentile | -1.25                                               | `r percentiles$Median` |
| 75th percentile | 3.86                                                | `r percentiles$Q3`     |

@@

## Blocking period length impact

Selecting different blocking periods affects the timing of evaluating
stopping criteria, thus influencing the duration of the measurement and
verification (M&V) process. Here, we summarize the advantages and
disadvantages of shorter versus longer blocking periods. As discussed in
our previous study, the second step of this randomized M&V method
involves choosing an appropriate blocking period to minimize potential
biases caused by 'bad' randomization. For most practical scenarios, we
recommend a blocking period of approximately 12 to 16 weeks, as it
typically covers the duration of a season, ensuring a representative
sampling of operational conditions. Opting for a shorter blocking
period, such as 6 weeks, has the potential benefit of allowing the
stopping criteria to be met earlier. However, this also means that the
analyst should perform the hypothesis tests more frequently. To avoid
false positive due to frequent testing, adjusting the significance level
using methods such as the Bonferroni correction can control for
increased type-I error risk [@vickerstaff_methods_2019]. Additionally, a
shorter blocking period can reduce the adverse impact of missing or
problematic data. For example, if the intervention requires fine-tuning
after initial implementation, removing data from the first blocking
period would have less damage compared to when the switchback experiment
was designed with longer blocking period. On the other hand, longer
blocking periods are advantageous when evaluating multiple intervention
strategies or using sampling intervals greater than one day. In such
cases, a longer block can more easily ensure a balanced distribution of
both day-of-week and outdoor weather conditions.
